---
title: "11_2homework"
author: "Zhaoji Wu, Fanghan Yang, Zhenhang Weng, Xiyu Fan"
date: "2021/11/1"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

Import the required packages during the experiment.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape2)
require(ggplot2)
require(ggthemes)
theme_set(theme_minimal())
require(GGally)
require(ggExtra)
require(maxLik)
require(knitr)
```

Load the data bright.Rdata, analyze and process this data
```{r Load_Data}
# paths
source("../../Code/R/imagematrix.R")
load("../../Data/Binary/bright.Rdata")
# Inspect what they are in the Environment window

typeof(bright)
dim(bright)
range(bright)

channal<-1
# vector.bright <- data.frame(as.vector(bright))
vector.bright <- data.frame(UHV=as.vector(bright[,,channal]))
summary(vector.bright)
```


Use imagematrix to display pictures(Including the original image, the processed function of the cumulative distribution, and the logarithm and normalized image)

```{r img_plot,fig.align = "center",fig.cap="bright image"}
plot(imagematrix(normalize(bright[,,channal])))
ecdf.bright <- ecdf(unlist(vector.bright))
eq.bright <- ecdf.bright(unlist(vector.bright))
dim(eq.bright) <- dim(bright[,,channal])
plot(imagematrix(eq.bright))
plot(imagematrix(normalize(log(bright[,,channal]))))
```
From the above figure, it can be seen that most of the data are clustered in the smaller area of x, resulting in a poor display of the first half of the densely distributed distribution.So We change the x-axis range and output again.Further we modify the bins of the histogram to make it more clearly displayed.

Draw a histogram of the data distribution and use different intervals to display the results. The data here is processed.
Histogram of the original data distribution
```{r Histogram,fig.align = "center",fig.cap="histogram"}
vector.bright <- data.frame(as.vector(bright))
ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright)),
                 col="blue", fill="black") +
  ylab("Density") +
  xlab("Intensity") 

ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright)),
                 col="blue", fill="black") +
  ylab("Density") +
  xlab("Intensity range:(0-2e6)") +
  xlim(0,2e6)


ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 alpha=0.5, 
                 col="blue",fill="black",
                 bins=nclass.FD(unlist(vector.bright))/100) +
  ylab("Histogram")+
  xlab("Intensity range:(0-2e6)") +
  xlim(0,2e6)
```


## The first distribution -- the (SAR) Gamma distribution

The distribution expression is $f_{\Gamma}(z;L,\mu)=\frac{L^{L}}{\mu^{L} \Gamma(L)} z^{L-1}exp{\{- \frac{Lz}{\mu}\}}$.

1.Moment Estimation (L=1)

$$
\begin{cases}
E(z)=\mu \\
Var(z)=\frac{\mu ^{2}}{L}=\mu^{2}
\end{cases}
$$

According to the above formula, we can get the estimated value of the parameter.

$$
\begin{cases}
\hat{\mu}=E(z)\\
\hat{L}=\frac{E(z)^2}{Var(z)}=1
\end{cases}
$$


2.Maximun Likelihood Estimation

The likelihood function is expressed as $g(Z;L,\mu)=\prod \limits_{i=0}^n f_{\Gamma}(z_{i};L,\mu)=\prod \limits_{i=1}^{n} \frac{L^{L}}{\mu^{L}\Gamma(L)} z_{i}^{L-1}exp{\{- \frac{Lz_{i}}{\mu}\}}=(\frac{L^{L}}{\mu^{L} \Gamma(L)})^{n} \cdot (\prod \limits_{i=1}^n z_{i})^{L-1}exp{\{- \frac{L}{\mu} \prod \limits_{i=1}^n z_{i}\}}$.
The logarithmic likelihood function is expressed as $ln(g(L,\mu))=n \cdot ln(\frac{L^{L}}{\mu^{L}\cdot\Gamma(L)})+(L-1)\sum\limits_{i=1}^{n} ln(z_{i})-\frac{L}{\mu}\sum\limits_{i=1}^n z_{i}$.

The maximum likelihood estimation of $\mu$ can be obtained by taking the derivative with respect to $\mu$ ($\frac{\partial ln(g(Z;L,\mu))}{\partial \mu}=n\cdot \frac{\mu^{L}\Gamma(L)}{L^{L-1}}\cdot(-\frac{L^{L}}{\Gamma(L)\mu^{L+1}})+\frac{L}{\mu^{2}}\sum\limits_{i=1}^nz_{i}$) and setting the partial derivative equal to 0 ($-\frac{n}{\mu}+\frac{1}{\mu^2}\sum\limits_{i=1}^nz_{i}=0$).

The estimate of parameter $\mu$ is $\frac{1}{n}\sum\limits_{i=1}^nz_{i}$.

## The second distribution -- the $G_{I}^{0}$ distribution



The distribution expression is $f_{Z}(z;\alpha,\gamma,L)=\frac{L^{L}\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma^(L) \Gamma(-\alpha)} \frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}}$.
The k-order moment of Z is expressed as $E(Z^{k})=(\frac{\gamma}{L})^k\frac{\Gamma(-\alpha-k)}{\Gamma(-\alpha)}\frac{\Gamma(L+k)}{\Gamma(L)}$.

1.Moment Estimation 

$$
\begin{cases}
E(z)=\frac{\gamma}{-\alpha-1} \\
Var(z)=E(z^{2})-(E(z))^{2}=\gamma^2\frac{\Gamma(-\alpha-2)}{\Gamma(-\alpha)}\frac{\Gamma(1+2)}{\Gamma(1)}=\frac{2\gamma^{2}}{(-\alpha-1)(-\alpha-2)}-(\frac{\gamma}{-\alpha-1})^{2}
\end{cases}
$$

By means of the above formulation, we can obtained the moment estimate of the parameter.

$$
\begin{cases}
E(z)=\frac{\gamma}{-\alpha-1} \\
Var(z)=\frac{\gamma^{2}\alpha}{(\alpha+1)^2(\alpha+2)}
\end{cases}
$$
According to the above formula, we can get the estimated value of the parameter.


$$
\begin{cases}
\alpha=-2-\frac{2(E(z))^2}{(E(z))^2+var(z)}\\
\gamma=E(z)\cdot(2+\frac{2(E(z))^2}{(E(z))^2+var(z)})
\end{cases}
$$



2.Maximun Likelihood Estimation

The likelihood function is expressed as $g(Z,1;\alpha,\gamma)=\prod \limits_{i=0}^n f_{Z}(z_{i};\alpha,\gamma,L)=\prod \limits_{i=1}^{n} \frac{L^{L}\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(L) \Gamma(-\alpha)} \frac{z_{i}^{L-1}}{(\gamma+Lz_{i})^{L-\alpha}}$.

The logarithmic likelihood function is expressed as $ln(g(Z,1;\alpha,\gamma))=ln\frac{\Gamma(1-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)}+\sum\limits_{i=1}^nln\frac{z_{i}}{\gamma+z_{i}}+\alpha\sum\limits_{i=1}^nln(\gamma+z_{i})=ln(-\alpha)-\alpha ln(\gamma)+\sum\limits_{i=1}^nlnz_{i}+(\alpha-1)\sum\limits_{i=1}^nln(\gamma+z_{i})$.

The maximum likelihood estimation of $\alpha$ and $\gamma$ can be obtained by taking the derivative with respect to $\alpha$ and $\gamma$ and setting the partial derivative equal to 0.

$$
\begin{cases}
\frac{\partial ln(g(Z,1;\alpha,\gamma))}{\partial \alpha}=\frac{1}{\alpha}-ln\gamma+\sum\limits_{i=1}^nln(\gamma+z_{i})=0\\
\frac{\partial ln(g(Z,1;\alpha,\gamma))}{\partial \gamma}=-\frac{\alpha}{\gamma}-(\alpha-1)\sum\limits_{i=1}^n\frac{1}{\gamma+z_{i}}=0
\end{cases}
$$

By simplifying the above equation, we can get:

$$
\begin{cases}
\alpha=\frac{1}{ln\gamma-\sum\limits_{i=1}^n ln(\gamma+z_{i})}=0\\
-\gamma+\sum\limits_{i=1}^n\frac{1}{\gamma+z_{i}}[1-ln\gamma+\sum\limits_{i=1}^nln(\gamma+z_{i})]=0
\end{cases}
$$

Obtained through the definition of the teacher github file
```{r dgammaSAR and dGI0}
#Chama as densid ades Gamma com os paramentros a parametrização do Modelo SAR de intensidade.
#Função para Densidade DgammaSAR.
#Entradas: x, Looks, mean

dgammaSAR <- function(x, Looks, mean) {
  
  dgamma(x, shape=Looks, rate=Looks/mean)
  
}


# Version 1: from scratch
dGI0 <- function(z, p_alpha, p_gamma, p_Looks, log=FALSE) {
  
  if(log==TRUE) {
    return(
      (p_Looks*log(p_Looks) + lgamma(p_Looks-p_alpha) + (p_Looks-1)*log(z) ) - 
        (p_alpha*log(p_gamma) + lgamma(-p_alpha) + lgamma(p_Looks) + 
        (p_Looks-p_alpha)*log(p_gamma + z*p_Looks) ) 
      )   
    }
  else { return( 
    ( p_Looks^p_Looks * gamma(p_Looks-p_alpha) * z^(p_Looks-1) ) / 
    (p_gamma^p_alpha * gamma(-p_alpha) * gamma(p_Looks) * (p_gamma + z*p_Looks)^(p_Looks-p_alpha)) 
  )
  }
}
```

According to the formula,define the method of obtaining parameters by Moments estimators and Maximum Likelihood estimators.
```{r Moments estimators}

# comparison

GI0.Estimator.m1m2 <- function(z, L) {
  m1 <- mean(z)
  m2 <- mean(z^2)
  m212 <- m2/m1^2
    
  a <- -2 - (L+1) / (L * m212)
  g <- m1 * (2 + (L+1) / (L * m212))
  
  return(list("alpha"=a, "gamma"=g))
}

```


```{r Maximum Likelihood estimators}
LogLikelihoodLknown <- function(params) {
  
  p_alpha <- -abs(params[1])
  p_gamma <- abs(params[2])
  p_L <- abs(params[3])
  
  n <- length(z)
  
  return(
    n*(lgamma(p_L-p_alpha) - p_alpha*log(p_gamma) - lgamma(-p_alpha)) + 
      (p_alpha-p_L)*sum(log(p_gamma + z*p_L)) 
  )
}
```


Use Moments estimators and Maximum Likelihood estimators to obtain the corresponding parameters to fit the curve.
```{r use Gamma model(L) G0 model(a,y) to fit bright.data,fig.align = "center",fig.cap="Fit a model"}
# comparison



vector.bright <- data.frame(UHV = as.vector(bright))

m<-mean(vector.bright$UHV)
L<-1


estim.Urban <- GI0.Estimator.m1m2(vector.bright$UHV, L)
z <- vector.bright$UHV
estim.UrbanML <- maxNR(LogLikelihoodLknown, 
                       start=c(estim.Urban$alpha, estim.Urban$gamma,1), 
                       activePar=c(TRUE,TRUE,FALSE))$estimate[1:2]

# comparison


a_estimate_1t <- estim.Urban$alpha
g_estimate_1t <- estim.Urban$gamma

a_estimate_2t <- estim.UrbanML[1]
g_estimate_2t <- estim.UrbanML[2]




intensity <- seq(0.001, 2e6, length.out = 1e5)

dExp <- dgammaSAR(intensity,Looks=L, mean=m)
dGI0Mom <- dGI0(intensity, p_alpha=a_estimate_1t, p_gamma=g_estimate_1t, p_Looks=L)
dGI0ML <- dGI0(intensity, p_alpha=a_estimate_2t, p_gamma=g_estimate_2t, p_Looks=L)



df.densities <- data.frame(intensity, dExp, dGI0Mom, dGI0ML)
densities.flat <- melt(df.densities, 
                       measure.vars = c("dExp", "dGI0Mom", "dGI0ML"))

names(densities.flat) <- c("Intensity", "Density", "value")

ggplot(data=vector.bright, aes(x=UHV)) +
  geom_histogram(aes(y=..density..), col="purple",

  bins=nclass.FD(unlist(vector.bright))/50) +

  geom_line(data=densities.flat, aes(x=Intensity, y=value, col=Density),
  lwd=1.5, alpha=.7) +
  xlab("Intensities from the bright") +
  ylab("Histogram, and fitted Exponential and G0 Laws") +
  ggtitle("Restricted Histogram and fitted densities") +
  theme_few()+

  xlim(0,2e6)
```
The red line is the result of using SAR Gamma estimator.  
The green line is the result of using G0 distribution combined with moment estimator.  
The blue line is the result of using the G0 distribution combined with maximum likelihood estimator.  