---
title: "SAR10_20"
author: "Zhenhang Weng,Xiyu Fan,Zhaoji Wu,Fanghan Yang"
date: "2021/10/18"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

First, import the R language file that supports the function run and import the packages that we need in the project(reshape2,ggplot2,ggthemes,GGally,ggExtra)
```{r setup,include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape2)
require(ggplot2)
require(ggthemes)
theme_set(theme_minimal())
require(GGally)
require(ggExtra)
source("Statistics-SAR-Intensity/Codes/imagematrix.R")
```

#The definition of K-Distribution.dKI is k-Distribution distribution function.rKI is used to create the random sample which obeys the k distribution.
```{r the define of K distribution function}
dKI <- function(z, p_alpha, p_lambda, p_Looks, log=FALSE) {
  
  if(log==FALSE) {
    
    lLz <- p_lambda * p_Looks* z
    
    return((2*p_lambda*p_Looks/(gamma(p_alpha)*gamma(p_Looks))) *
             (lLz)^((p_alpha+p_Looks)/2-1) *
             besselK(x = 2*sqrt(lLz), nu = p_alpha-p_Looks)
    )
  }
  
}


rKI <- function(n, p_alpha,p_lambda, p_Looks) {
  
  return(
    rgamma(n, 1, p_Looks)*rgamma(n, p_alpha/p_lambda, p_alpha)
  )
  
}
```

#The definition of G0 distribution.dGI0 is G0-Distribution distribution function.rGI0 is used to create the random sample which obeys the GO distribution.

```{r the define of G0 distribution function}
dGI0 <- function(z, p_alpha, p_gamma, p_Looks, log=FALSE) {
  
  if(log==TRUE) {
    return(
      (p_Looks*log(p_Looks) + lgamma(p_Looks-p_alpha) + (p_Looks-1)*log(z) ) - 
        (p_alpha*log(p_gamma) + lgamma(-p_alpha) + lgamma(p_Looks) + 
        (p_Looks-p_alpha)*log(p_gamma + z*p_Looks) ) 
      )   
    }
  else { return( 
    ( p_Looks^p_Looks * gamma(p_Looks-p_alpha) * z^(p_Looks-1) ) / 
    (p_gamma^p_alpha * gamma(-p_alpha) * gamma(p_Looks) * (p_gamma + z*p_Looks)^(p_Looks-p_alpha)) 
  )
  }
}


rGI0 <- function(n, p_alpha, p_gamma, p_Looks) {
  
  return(
    rgamma(n, 1, p_Looks) / rgamma(n, -p_alpha, p_gamma)
  )
  
}
```



Firstly we create the data s which is from 0.001 to 10.Then according to the K function completed in the previous section, here we give the images of functions with (alpha, lambda, looks) of (2, 1, 1) in purple, (4, 5, 2) is green, (6, 9, 3) in red .
```{r K distribution for intensity data,fig.align = "center",fig.cap="K distribution"}
s <- seq(0.001, 10, length.out = 500)
s <- data.frame(s)
ggplot(data=s, aes(x=s),
       y=Transformations, 
       color=Transformation) +
  stat_function(fun=dKI, geom = "line", size=2, col="purple", args = list(p_alpha=2, p_lambda=1, p_Looks=1)) +
  stat_function(fun=dKI, geom = "line", size=2, col="green", args = list(p_alpha=4, p_lambda=5, p_Looks=2)) +
  stat_function(fun=dKI, geom = "line", size=2, col="red", args = list(p_alpha=6, p_lambda=9, p_Looks=3)) +
  xlab("x") + 
  ylab("y") +
  labs(title = "K Distribution") +
  scale_x_log10()
```

Using the same data s as in the previous section.The G0 function defined according to the previous completion，here we give the images of functions with (alpha, lambda, looks) of (2, 1, 1) in  purple, (4, 5, 2) in green, (6, 9, 3) in red respectively.
```{r G0 distribution for intensity data,fig.align = "center",fig.cap='G0 distribution'}
s <- seq(0.001, 10, length.out = 500)
s <- data.frame(s)
ggplot(data=s, aes(x=s)) +
  stat_function(fun=dGI0, geom = "line", size=2, col="purple", args = list(p_alpha=-2, p_gamma=1, p_Looks=1)) +
  stat_function(fun=dGI0, geom = "line", size=2, col="green", args = list(p_alpha=-4, p_gamma=5, p_Looks=2)) +
  stat_function(fun=dGI0, geom = "line", size=2, col="red", args = list(p_alpha=-6, p_gamma=9, p_Looks=3)) +
  xlab("x") + 
  ylab("y") +
  labs(title = "G0 Distribution") +
  scale_x_log10()
```


Using rKI to generate random numbers obeying parameter which alpha=4 ,lambda=5,Looks=2,num=100000.And show the data we create in histogram and Histogram & smoothed histogram. 
```{r K distribution random generator,fig.align='center',fig.cap='random number generators for K distribution'}
p_alpha=4
p_lambda=5
p_Looks=2
pk_num=100000

#Histogram & smoothed histogram
s <- rKI(pk_num, p_alpha, p_lambda, p_Looks) 
s <- data.frame(s) # x~K(p_alpha, p_lambda, p_Looks)

ggplot(data=s, aes(x=s)) +
  geom_histogram(aes(y=..density..),alpha=0.5, fill="#6495ED",color="black",bins=nclass.FD(unlist(s))/10) +
  geom_density(col="red", size=1) +
  geom_boxplot(aes(y=1), width=.1)+
  stat_ecdf(col="purple") +
  xlab("x") +
  ylab("y") +
  labs(title="Histogram & smoothed histogram") +
  scale_x_log10()

```


Comparing the k distribution with two different gamma distributions,the purple line shows the distribution of dgamma fuction with shape=1, scale=p_Looks,the green one is the  dgamma fuction with shape=p_alpha/p_lambda, scale=p_alpha).
```{r Composition of K distribution,fig.align='center',fig.cap='Composition of K distribution'}
s <- seq(0.001, 10, length.out = 500) 
s <- data.frame(s)
ggplot(data=s, aes(x=s)) +
  stat_function(fun=dgamma, geom = "line", size=2, col="purple", args = list(shape=1, scale=p_Looks)) +
  stat_function(fun=dgamma, geom = "line", size=2, col="green", args = list(shape=p_alpha/p_lambda, scale=p_alpha)) +
  stat_function(fun=dKI, geom = "line", size=2, col="red", args = list(p_alpha=p_alpha, p_lambda=p_lambda, p_Looks=p_Looks)) +
  xlab("x") +
  ylab("y") +
  labs(title = "R-gamma(1,L), B-gamma(a/l,a), G-K(a,l,L)") +
  scale_x_log10()
```
In first picture, Histograms/smoothed histogram are generated using the K-distribution random number generator

In second picture, the red line represents the curve the K distribution curve,the green line and the purple line respectively represent two Gamma distribution that generate the K-distribution 

Using rGI0 to generate random numbers obeying parameter which alpha=-4 ,lambda=5,Looks=2,num=100000.And show the data we create in histogram and Histogram & smoothed histogram. 
```{r G0 distribution random generator,fig.align='center',fig.cap='random number generators for G0 distribution'}
p_alpha=-4
p_gamma=5 
p_Looks=2
pG0_num=100000

# Histogram & smoothed histogram
s <- rGI0(pG0_num,p_alpha, p_gamma, p_Looks)
s <- data.frame(s) # x~G0(p_alpha, p_gamma, p_Looks)

ggplot(data = s, aes(x=s)) +
  geom_histogram(aes(y=..density..),alpha=0.5, fill="#6495ED",color="black",bins=nclass.FD(unlist(s))/10) +
  geom_density(col="red", size=1) +
  geom_boxplot(aes(y=1), width=.1)+
  stat_ecdf(col="purple") +
  xlab("x") +
  ylab("y") +
  labs(title = "Histogram & smoothed histogram") +
  scale_x_log10()
```
In first picture, Histograms/smoothed histogram are generated using the G0-distribution random number generator

In second picture, the red line represents the curve the G0-distribution curve,the green line and the purple line respectively represent two Gamma distribution that generate the G0-distribution 

Comparing the G0 distribution with two different gamma distributions,the purple line shows the distribution of dgamma fuction with shape=1, scale=p_Looks,the green one is the  dgamma fuction with shape=p_alpha/p_lambda, scale=p_alpha).
```{r Composition of G0 distribution,fig.align='center',fig.cap='Composition of G0 distribution'}
s <- seq(0.001, 10, length.out = 500) 
s <- data.frame(s)
ggplot(data=s, aes(x=s)) +
  stat_function(fun=dgamma, geom = "line", size=2, col="purple", args = list(shape=1, scale=p_Looks)) +
  stat_function(fun=dgamma, geom = "line", size=2, col="green", args = list(shape=-p_alpha, scale=p_gamma)) +
  stat_function(fun=dGI0, geom = "line", size=2, col="red", args = list(p_alpha=p_alpha, p_gamma=p_gamma, p_Looks=p_Looks)) +
  xlab("x") + 
  ylab("y") +
  labs(tittle = "R-gamma(1,L), B-gamma(-a,g), G-G0(a,g,L)") +
  scale_x_log10()
```

The image of dgamma and pgamma function with the shape in 1,4,9 is shown followed.And the same times,we also give the histogram of them.
```{r dgamma Distributions use our choice,fig.align = "center",fig.cap='dgamma distribution'}
s <- seq(0.001, 10, length.out = 500)
s <- data.frame(s)
ggplot(data=s, aes(x=s)) +
  stat_function(fun=dgamma, geom = "line", size=2, col="purple", args = list(shape=1, scale=1)) +
  stat_function(fun=dgamma, geom = "line", size=2, col="green", args = list(shape=4, scale=1/4)) +
  stat_function(fun=dgamma, geom = "line", size=2, col="red", args = list(shape=9, scale=1/9)) +
  xlab("x") + 
  ylab("y") +
  labs(title = "dgamma Distribution") +
  scale_x_log10()
```


```{r dgamma Distributions histogram,fig.align='center',fig.cap='dgamma distribution'}
s <- seq(0.001, 10, length.out = 500)
a_1 <- dgamma(s,1,1)
a_1 <- data.frame(a_1)
ggplot(data=a_1, aes(x=s)) +
  geom_histogram(aes(y=..density..),
                 bins=30,
                 col="black", fill="white")+
  xlab('x')+
  ylab("density")+
  labs(title = "dgamma Distribution")
```


```{r pgamma Distributions use our choice,fig.align = "center",fig.cap="pgamma distribution"}
s <- seq(0.001, 10, length.out = 500)
s <- data.frame(s)
ggplot(data=s, aes(x=s)) +
  stat_function(fun=pgamma, geom = "line", size=2, col="purple", args = list(shape=1, scale=1)) +
  stat_function(fun=pgamma, geom = "line", size=2, col="green", args = list(shape=4, scale=1/4)) +
  stat_function(fun=pgamma, geom = "line", size=2, col="red", args = list(shape=9, scale=1/9)) +
  xlab("x") + 
  ylab("y") +
  labs(title = "pgamma Distribution")

```


```{r pgamma Distributions histogram,fig.align='center',fig.cap='pgamma distribution'}
s <- seq(0.001, 10, length.out = 500)
a_1 <- pgamma(s,1,1)
a_1 <- data.frame(a_1)
ggplot(data=a_1, aes(x=s)) +
  geom_histogram(aes(y=..density..),
                 bins=30,
                 col="black", fill="white")+
  xlab('x')+
  ylab("density")+
  labs(title = "pgamma Distribution")
```

#__Analyze the bright image data__
```{r load brigrt.Rdata,include=FALSE}
load("../Statistics-SAR-Intensity/Data/R/bright.Rdata")
```

The basic information of the bright data is shown here, including dimensions, data types and ranges, etc.
```{r analize the data,collapse=TRUE,prompt=TRUE,comment=''}
dim(bright)
typeof(bright)
range(bright)
```


```{r change the type of data}
bright_data <- data.frame(bright=as.vector(bright))
summary(bright_data)
```
We use boxplot to analyze the inner information of the data, the outliers are shown in red.  
In order to better analyze the data, we also apply a logarithmic transformation to the data.

```{r Exploratory Data Analysis_Boxplot, fig.cap='Boxplots with notches', fig.subcap=c('Linear scale', 'Semilogarithmic scale'),fig.align = "center"}
ggplot(bright_data, aes(x=bright)) +
  geom_boxplot(notch = TRUE)+
  geom_boxplot(outlier.colour="red", outlier.shape=21,outlier.size=1)+
  ggtitle("Boxplot of bright")+
  ylab("Boxplot")

ggplot(bright_data, aes(x=bright)) +
  geom_boxplot(notch = TRUE) +
  geom_boxplot(outlier.colour="red", outlier.shape=21,outlier.size=1)+
  scale_x_log10()+
  ylab("Boxplot") +
  ggtitle("Boxplot of bright(semilog scale)")
```

As is shown in the first picture, we can see from the “bright” figure, the box is so flattened.  
After using a logarithmic transformation, the average value of the data is around 10^5 with little fluctuation.


And then, we use histogram to show the structure of the data. By using different bins we get first and second picture.  
Here, we also use semilog scale, which is shown in the third one.

```{r Exploratory Data Analysis_Histogram, fig.cap='Histogtram', fig.subcap=c('Linear scale', 'Semilogarithmic scale'), fig.align='center'}
hist(bright,freq = FALSE)
lines(density.default(bright),col='blue')
ggplot(bright_data, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(bright_data)),
                 col="black", fill="white")+
  xlab("Intensity")+
  ylab("Density") +
  ggtitle("Histogram of bright")
ggplot(bright_data, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(bright_data)),
                 col="black", fill="white") +
  scale_x_log10()+
  xlab("Intensity in semilogarithmic scale")+
  ylab("Density") +
  ggtitle("Histogram of bright(semilog scale)")
```

We can see, after using semilog scale, the data is distributed more widely, which means better analysis.  

After this part of analysis, we put boxplot and histogram together.  
We can obtain the following information:  
1. The data are positive.  
2. The data have a very large dynamic range.  
3. The data are symmetric at its mean.  

```{r Exploratory Data Analysis_Histogram+Boxplot,fig.cap='Histogtram+Boxplot',fig.align='center'}
ggplot(bright_data, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(bright_data)),
                 col="black", fill="white") +
  geom_boxplot(aes(y=1.0), width=.1, notch=TRUE,outlier.colour="red", outlier.shape=21,outlier.size=1) +
  #geom_boxplot(outlier.colour="red", outlier.shape=21,outlier.size=1)+
  ylab("Density and Boxplot") +
  xlab("Intensity in semilogarithmic scale") +
  scale_x_log10()
```
In this part we can see the original data and its empirical function.

```{r Empirical Function+Histogram,fig.align='center'}
ggplot(bright_data, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(bright_data)),
                 col="black", fill="white") +
  stat_ecdf(col="red") +
  ylab("Density and Empirical function") +
  xlab("Intensity in semilogarithmic scale") +
  scale_x_log10()
```

After all of the analysis, now, let's use the bright data to generate a image, the “imagematrix” library provides a function to help us.

```{r Image,fig.align='center'}
plot(imagematrix(normalize(bright)))
```


